---
title: "fb_dogs_anticipatory looking"
author: "Lucrezia Lonardo"
date: "10/02/2021"
output: html_document
---
#load functions
```{r}
rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(glmmTMB)
#library(sjPlot)
source("../functions/diagnostic_fcns.r")
source("../functions/glmm_stability.r")
source("../functions/boot_glmm.r")
```

#import data
```{r setup, include=FALSE}
xdata <- read.csv(file="../data/Dataset_S5_exp1_ant_look.csv")
```
#GLMM investigating the effect of condition on anticipatory looking. Table S3
```{r cars}
xx.fe.re=fe.re.tab(fe.model="ant_look ~ condition + age + sex + first_baited_box",
                   re="(1|breed)", data=xdata)				   
model.data=xx.fe.re$data
str(model.data)
```

#centering the dummy variable for sex, condition and first baited box
```{r pressure, echo=FALSE}
model.data <- xdata %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(sex), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(condition), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(first_baited_box), scale=F, center=T)))

as.data.frame(model.data)
```
#running the model
```{r}
full.ant.look.breed <- glmer(ant_look ~ condition + z.age + sex + first_baited_box+
             (1+ sex.c + condition.c + first_baited_box.c + z.age|| breed), 
             data = model.data, family = binomial, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```
# estimate; std. error; z-value
```{r}
round(summary(full.ant.look.breed)$coefficients, 3)
```
#p values
```{r}
tests=as.data.frame(drop1(full.ant.look.breed, test="Chisq"))
round(tests,3) 

```
#confidence intervals
```{r}
boot.res=boot.glmm.pred(model.res=full.ant.look.breed, excl.warnings=T,
	nboots=1000, para=T)
round(boot.res$ci.estimates, 3) #the model is not robust at all, probably due to the small sample

```
# random effect (breed)
```{r}
summary(full.ant.look.breed)$varcor # the contribution of breed ( std. dev. 0.000 )is smaller than that of condition (estimate:  -0.728)
```
#check for collinearity (it can only be assessed for standard linear models) 
```{r}
col.full.ant.look.breed <- lm(ant_look ~ condition + z.age + sex + first_baited_box, data = model.data)
vif(col.full.ant.look.breed) #they are all 1, no problem
```
# check whether BLUPs (Best Linear Unbiased Predictors: estimated deviations of intercepts and slopes from the respective common average, per level of the random effects) are normally distributed
```{r}
ranef.diagn.plot(full.ant.look.breed)
```
#model stability
```{r}
m.stab=glmm.model.stab(model.res=full.ant.look.breed, contr=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

names(m.stab)
table(m.stab$detailed$warnings) # all models converged (27 breeds)

#summary reveals min and max of the estimates obtained after case-wise deletion of levels of random effects, together with the original estimates

round(m.stab$summary[,-1],3)
# the effect of condition seems to be pretty stable even when excluding one breed at a time: 
#conditionTrueBelief  orig: -0.728 min: -1.236 max: -0.366

m.stab.plot(m.stab$summary[, -1])
```
#ant_look plot FCI groups
```{r}
fb_data <- read_csv("../data/Dataset_S5_exp1_ant_look.csv")
view(fb_data)

plot.data.fci <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))%>% #renaming of factor levels
  group_by(condition, fci_group)%>%
  summarise(mean.ant_look=mean(ant_look), sd.ant_look=sd(ant_look), sum.ant_look=sum(ant_look), median.ant_look=median(ant_look), n.ant_look=length(ant_look), se.ant_look=sd(ant_look)/sqrt(length(ant_look)))

#change facet labels
fci.labs <- c("FCI group 1","FCI group 2","FCI group 3","FCI group 5","FCI group 6","FCI group 7","FCI group 8","FCI group 10")
plot.data.fci$fci_group<-as.factor(plot.data.fci$fci_group)
names(fci.labs) <- c(levels(plot.data.fci$fci_group))


p.ant.look.fci<-ggplot(
  data=plot.data.fci, aes(x=condition, y=mean.ant_look)) +
  geom_bar(stat="identity", alpha=0.5)+
  geom_errorbar(aes(ymin=mean.ant_look-se.ant_look, ymax=mean.ant_look+se.ant_look), width=.2) +
  geom_text(aes(x=condition, y=-0.15, label=n.ant_look), vjust=0,  size=3.5)+
  ylim(-0.15,1)+
  theme_classic()+
  labs(x="Condition",y="Proportion dogs anticipating bucket B")+
  facet_wrap(~fci_group, ncol=2, labeller=labeller(fci_group=fci.labs))
  
p.ant.look.fci

#save the plot 
ggsave(
  "FigureS7_ant_look_FCI_groups.pdf",
  plot = last_plot(),
  device = NULL,
  path = "../graphs",
  scale = 1,
  width = 4,
  height = 7,
  units = c("in", "cm", "mm"),
  dpi = 320,
  limitsize = TRUE
)

```

