---
title: "False Belief Task 2020"
author: ""
date: "July 22, 2020"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(glmmTMB)
#library(sjPlot)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")


#install.packages("")

#load(file ="mm1_mult_poss.RData")



```
#import data
```{r loading data, include = FALSE}
fb_data <- read.csv(file="data/Dataset_S1.csv")
```
# LMM (function lmer) with breed as a random intercept: effect of condition on latency (log transformed). Table S2


#centering and scaling variables
```{r}
xx.fe.re=fe.re.tab(fe.model="latency ~ condition + age + sex + first_baited_box",
                   re="(1|breed)", data=fb_data)				   
model.data=xx.fe.re$data
str(model.data)

#centering the dummy variable for sex, condition and first baited box
model.data <- fb_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(sex), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(condition), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(first_baited_box), scale=F, center=T)))
#log transform latency
model.data$log.latency<-log(model.data$latency)
```
#running the model
```{r}
full.latency.breed <- lmer(log.latency ~ condition + z.age + sex + first_baited_box+
             (1+ sex.c + condition.c + first_baited_box.c + z.age || breed), 
             data = model.data)
```
#estimate; std. error; z-value
```{r}
round(summary(full.latency.breed)$coefficients, 3)
```
#p-values. + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
drop1.full=drop1(full.latency.breed, test="Chisq")
round(drop1.full,3)
```
#confidence intervals
```{r}
boot.res=boot.glmm.pred(model.res=full.latency.breed, excl.warnings=T,
	nboots=1000, para=T)
round(boot.res$ci.estimates, 3) 
```
#random effects (breed)
```{r}
summary(full.latency.breed)$varcor # the contribution of breed ( intcpt std. dev. 0.34022 )is larger than that of condition (estimate: 0.019 )
```
#check for collinearity (it can only be assessed for standard linear models) 
```{r}
col.full.latency.breed <- lm(latency ~ condition + z.age + sex + first_baited_box, data = model.data)
vif(col.full.latency.breed) #they are all 1, no problem
```
#check whether the residuals are normally distributed and homogeneous
```{r}
#diagn.pl<-
diagnostics.plot(full.latency.breed) 
```
# check whether BLUPs (Best Linear Unbiased Predictors: estimated deviations of intercepts and slopes from the respective common average, per level of the random effects) are normally distributed
```{r}
ranef.diagn.plot(full.latency.breed)
```
#model stability
```{r}
m.stab=glmm.model.stab(model.res=full.latency.breed, contr=NULL, para=T, data=NULL)

names(m.stab)
table(m.stab$detailed$warnings) # all models converged (36 breeds)
#summary reveals min and max of the estimates obtained after case-wise deletion of levels of random effects, 
#together with the original estimates

round(m.stab$summary[,-1],3)
# the effect of condition is quite stable when excluding one breed at a time: 
#conditionTrueBelief  orig: 0.019 min: -0.037  max: 0.073

m.stab.plot(m.stab$summary[, -1])
```






