---
title: "False Belief Task 2020"
author: ""
date: "July 22, 2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(sjPlot)
source("../functions/diagnostic_fcns.r")
source("../functions/glmm_stability.r")
source("../functions/boot_glmm.r")
```

```{r loading data, include = FALSE}
fb_data <- read.csv(file="../data/Dataset_S4_exp1_144dogs.csv")
```

### probability of first trial of 2nd familiarisation phase to be correct (following communicator's suggestion)
```{r}
binom.test(x=sum(fb_data$first_trial_fam), n=length(fb_data$first_trial_fam), p=0.5, alternative="two.sided")
```

 Choice performance according to the FCI groups
```{r}

plot.data.fci <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))%>% #renaming of factor levels
  mutate(correct=as.numeric(ifelse(choice=="baited",1,ifelse(choice=="empty",0,""))))%>%
  group_by(condition, fci_group)%>%
  summarise(mean.correct=mean(correct), sd.correct=sd(correct), sum.correct=sum(correct), median.correct=median(correct), n.correct=length(correct), se.correct=sd(correct)/sqrt(length(correct)))


p.choice.fci<-ggplot(
  data=plot.data.fci, aes(x=condition, y=mean.correct)) +
  geom_bar(stat="identity", alpha=0.5)+
  geom_errorbar(aes(ymin=mean.correct-se.correct, ymax=mean.correct+se.correct), width=.2) +
  ylim(0,1)+
  theme_classic()+
  labs(x="Condition",y="Proportion of baited bucket choices")+
  facet_wrap(~fci_group)
  
p.choice.fci
 
```
```{r}
# centering variables for modeling

model.data <- fb_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(as.factor(sex)), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(as.factor(condition)), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(as.factor(first_baited_box)), scale=F, center=T)))

as.data.frame(model.data)
```

GLMM02  with breed and communicator's identity as random interceptS (Table S4)

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ condition + age + sex + first_baited_box",
                   re="(1|breed)+(1|communicator)", data=fb_data)
xx.fe.re$summary
```
``` {r mixed modeling, error=TRUE}

## code to run the model
full.choice.breed <- glmer(correct ~ condition + z.age + sex + first_baited_box+
             (1+ sex.c + condition.c + first_baited_box.c + z.age| fci_group), 
             data = model.data, family = binomial, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```


####Model output
  + Coefficients
```{r}
round(summary(full.choice.breed)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.choice.breed, test="Chisq")
round(drop1.full,3)
```
```{r}
summary(full.choice.breed)$varcor
```

``` {r mixed modeling, error=TRUE}
#confidence intervals
boot.res=boot.glmm.pred(model.res=full.choice.breed, excl.warnings=T,
	nboots=1000, para=T)
res<-round(boot.res$ci.estimates, 3) 
res
```



## plot models

```{r}

library(sjmisc)
plot_model(full.choice.breed,  type = "re", vline.color = "red")

get_model_data(full.choice.breed, type = "re", show.values = T) 

plot_model(full.choice.breed, type = "est", show.values = TRUE)

sjp.lmer(full.choice.breed)

```
