---
title: "False Belief Task 2020"
author: ""
date: "July 22, 2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

library(lme4)
library(ggthemes)
library(psych)
library(summarytools)
library(cowplot)
library(car)
library(tidyverse)
library(ggsignif)
library(ggplot2)
library(dplyr)
#library(sjPlot)
source("functions/diagnostic_fcns.r")
source("functions/glmm_stability.r")
source("functions/boot_glmm.r")


#install.packages("")

#load(file ="mm1_mult_poss.RData")



```

```{r loading data, include = FALSE}
fb_data <- read.csv(file="data/Dataset_S1.csv")%>%
  mutate(fci_group = as.factor(fci_group))
```
### Plotting latencies: Figure S3
```{r}

plot.data.latency <- fb_data %>%
  mutate(condition=recode(condition, "FalseBelief"="False Belief", "TrueBelief"="True Belief"))#renaming of factor levels

p.latency<-ggplot(
  data=plot.data.latency, aes(x=condition, y=log(latency))) +
  geom_boxplot(alpha=0.5)+
  theme_classic()+
  labs(x="Group",y="Latency (log transformed)")
  
p.latency
#saving the plot 
ggsave("Fig_S3_exp1_latency_120dogs.pdf",
  plot = last_plot(),
  device = NULL,
  path = "~/R/data_code_Lonardo_et_al/graphs",
  scale = 0.7,
  width = 7,
  height = 5,
  #units = c("in", "cm", "mm"),
  dpi = 320,
  limitsize = TRUE
)
```
### GLMM
``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- fb_data %>% 
  mutate(z.age = as.numeric(scale(age, scale = T, center = T)),
         sex.c = as.numeric(scale(as.numeric(as.factor(sex)), scale=F, center=T)),
         condition.c = as.numeric(scale(as.numeric(as.factor(condition)), scale=F, center=T)),
         first_baited_box.c = as.numeric(scale(as.numeric(as.factor(first_baited_box)), scale=F, center=T)))

as.data.frame(model.data)
#view(dfSummary(model.data))
```
#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.full <- lm(correct ~ condition + z.age + sex + first_baited_box, data = model.data)
vif(col.full)
#no problem
```
### GLMM 01:Model with breed as random intercept. Table S1

```{r eval=FALSE, echo=FALSE}
xx.fe.re=fe.re.tab(fe.model="correct ~ condition + age + sex + first_baited_box",
                   re="(1|breed)", data=fb_data)
xx.fe.re$summary
```

``` {r mixed modeling, error=TRUE}

## code to run the model
full.choice.breed <- glmer(correct ~ condition + z.age + sex + first_baited_box+
             (1+ sex.c + condition.c + first_baited_box.c + z.age|| breed), 
             data = model.data, family = binomial, 
             control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

####Model output
  + Coefficients
```{r}
round(summary(full.choice.breed)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 

```{r}
drop1.full=drop1(full.choice.breed, test="Chisq")
round(drop1.full,3)
```
```{r}
summary(full.choice.breed)$varcor
```
#confidence intervals

```{r}
boot.res=boot.glmm.pred(model.res=full.choice.breed, excl.warnings=T,
	nboots=1000, para=T)
res<-round(boot.res$ci.estimates, 3)
res
```


```{r eval=FALSE, include=FALSE}
# Model stability
# One breed at a time excluded to assess the impact of outliers. 

m.stab.b <- glmm.model.stab(model.res = full.choice.breed, use = c("breed"))
m.stab.b$detailed$warnings
xx <- as.data.frame(round(m.stab.b$summary[, -1], 3))
xx
png("graphs/exp1_choice_stability_plot.png")
m.stab.plot(round(m.stab.b$summary[, -1], 3))
dev.off()

```


